Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-23 paper/ms.tex
Add reminder to fill in numbers

For an error in the $x$ component (or Solar radius), the
95\textsuperscript{th} minus 5\textsuperscript{th} percentiles are $x$, $y$,
and $z \actunit$ for $J_r$, $L_z$ and $J_z$, respectively. These are
fractional errors of $x\%$, $y\%$ and $z\%$, respectively.

>>>>

\Gus{For an error in the $x$ component (or Solar radius)}, the
95\textsuperscript{th} minus 5\textsuperscript{th} percentiles are $x$, $y$,
and $z \actunit$ for $J_r$, $L_z$ and $J_z$, respectively. These are
fractional errors of $x\%$, $y\%$ and $z\%$, respectively.
